Degrees Draft Syllabus

### 2023-04-02 Draft Syllabus.Rmd
adjusting title of png to try and get it to display

During the course you are going to work primarily in R and much of the work done using R will be done with R Markdown. Though there are many other languages used for data analysis (including Python, SAS, Stata, and SQL), you will not explore those. If you'd like to know more about one of them feel free to reach out to me and I am happy to share what I know or help point you to a starting place if I am inexperienced in the language myself. And it is okay to be inexperienced! Don't worry if you are not familiar with the language or with coding at all; this class and the Codecademy course that will supplement it are meant for beginners. If you do have experience with R and feel that the course is moving too slowly or that you are not being sufficiently challenged, I encourage you to 1) Add complexity to the examples and challenges presented in class or on Codecademy, 2) Visit some of the pages provided in the enrichment section of this syllabus, 3) read ahead in the syllabus and work on something that is at your level, or 4) focus extra time on your project.

>>>>

During the course you are going to work primarily in R and much of the work done using R will be done with R Markdown. Don't worry if you are not familiar with the language or with coding at all; this class and the Codecademy course that will supplement it are meant for beginners. If you do have experience with R and feel that the course is moving too slowly or that you are not being sufficiently challenged, I encourage you to 1) Add complexity to the examples and challenges presented in class or on Codecademy, 2) read ahead in the syllabus and work on something that is at your level, or 3) focus extra time on your project. Though there are many other languages used for data analysis (including Python, SAS, Stata, and SQL), you will not explore those. If you'd like to know more about one of them feel free to reach out to me and I am happy to share what I know or help point you to a starting place if I am inexperienced in the language myself.
